The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-10-15 OA.tex
edits of figures before submission
revision after jpe submission

\begin{figure}[H]
     \caption{Some Pawnshops}
    \label{PawnshopPicture}
    \begin{center}
    \begin{subfigure}{0.42\textwidth}
    \caption{Appraiser/tellers inside a pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio9.png}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio11.png}
    \end{subfigure}

@@

    \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio2.png}
    \end{subfigure}
    \begin{subfigure}{0.42\textwidth}
    \caption{Lost pawns which are for sale}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio3.png}
    \end{subfigure}
    \end{center}
    \scriptsize
        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
\end{figure}

\vspace{.1in}
\begin{figure}[H]
     \caption{Gold buyers next to pawnshops}
    \label{GoldBuyers}
    \begin{center}
    \begin{subfigure}{.49\textwidth}
    \caption{Gold buyer next to pawnshop 1}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio7.png}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
    \caption{Gold buyer next to pawnshop 1}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio8.png}
    \end{subfigure}
       \vspace{3ex}

@@

      The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment. Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm. 
%\textit{Do file: } \texttt{determinants_choice_sure_confidence.do}       
\end{figure}

@@

    \begin{center}
       \begin{subfigure}{0.49\textwidth}
        \caption{APR benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_apr.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
        \caption{Financial benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_fc_admin.pdf}
    \end{subfigure} 
    \end{center}
    \scriptsize This figure show the distribution of treatment effects under rank invariance
    \[F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u\]
where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.
    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
    % \texttt{fosd_ecdf.do}}
\end{figure}

@@

@@

      The above figure shows the determinants in a bivariate and multivariate OLS regression of sure confidence among the non-choosers. Sure confidence is a binary variable defined to be one when people report a 100\% probability of recovery.
%\textit{Do file: } \texttt{determinants_choice_sure_confidence.do}       
\end{figure}

@@

We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.  We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a training set and a test set.
These sets are constructed to ensure that all observations from a given branch-day cluster are allocated to the same set.
This avoids inferential problems that could arise from correlated unobservables within clusters.
In the first step, we apply the generalized random forest approach of \cite{atheygrf} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
\[
\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
\]
The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step. In particular, we estimate 
\begin{equation}
Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
\label{eq:chernreg}
\end{equation}
where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights. Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
\[
\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
\]
If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. 
Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
Our estimate for $\beta_2$ is 1.68 with a one-sided heteroskedasticity-robust (HC3) of 0.50.
Thus we easily reject the null hypothesis of homogeneous treatment effects.

@@

The \cite{huber_mellace} bounds for the TOT \& TUT APR are respectively:  $[-366, 490]$, and $[-19, 109]$.
Since both TUT (24) and ToT (122) estimates from the LATE approach lies inside these bounds, we cannot falsify the exclusion restriction. Moreover, the p-values associated with testing violation of inequalities \ref{eq:testable0}, and \ref{eq:testable1} is equal to one in both cases\footnote{We include the implementation of the validity test for the exclusion restriction for choosers and non-choosers in our STATA package.}.

@@

\begin{figure}[H]
        \caption{Example Causal Tree}
    \label{causal_tree1}
    \begin{center}
        \centering
        \includegraphics[width=\textwidth]{Figuras/crf_pro_2_apr.pdf}
    \end{center}
    \footnotesize 
    This figure shows an example of one of the regression trees used to compute the causal forest estimates described in Section \ref{sec:RF}. Each tree is constructed from a sequence of recursive binary partitions of the covariate space, with a splitting rule that is targeted to the causal quantity of interest, following the methodology of \cite{atheygrf}.
    %This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the fee-forcing contract. It is meant only as an example of how these trees look like. The forest was such that there are as many estimated treatment effects as there are clients.
     %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
\end{figure}

>>>>

\begin{figure}[H]
     \caption{Some Pawnshops}
    \label{PawnshopPicture}
    \begin{center}
    \begin{subfigure}{0.42\textwidth}
    \caption{Appraiser/tellers inside a pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio9_.png}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio11_.png}
    \end{subfigure}

@@

    \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
    \end{subfigure}
    \begin{subfigure}{0.42\textwidth}
    \caption{Lost pawns which are for sale}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
    \end{subfigure}
    \end{center}
    \scriptsize
        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
\end{figure}

\vspace{.1in}
\begin{figure}[H]
     \caption{Gold buyers next to pawnshops}
    \label{GoldBuyers}
    \begin{center}
    \begin{subfigure}{.49\textwidth}
    \caption{Gold buyer next to pawnshop 1}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio7_.png}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
    \caption{Gold buyer next to pawnshop 1}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio8_.png}
    \end{subfigure}
       \vspace{3ex}

@@

      The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment. Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm. 
%\textit{Do file: } \texttt{determinants_choice.do}       
\end{figure}

@@

    \begin{center}
       \begin{subfigure}{0.49\textwidth}
        \caption{APR benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_apr.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
        \caption{Financial benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_fc_admin.pdf}
    \end{subfigure} 
    \end{center}
    \scriptsize This figure show the distribution of treatment effects under rank invariance
    \[F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u\]
where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.
    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
    % \texttt{te_rankinvariance.do}}
\end{figure}

@@

\subsection{Sure Confidence} \label{App_sureconfidence}

@@

      The above figure shows the determinants in a bivariate and multivariate OLS regression of sure confidence among the non-choosers. Sure confidence is a binary variable defined to be one when people report a 100\% probability of recovery.
%\textit{Do file: } \texttt{determinants_sure_confidence.do}       
\end{figure}

@@

We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.  We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a training set and a test set.
These sets are constructed to ensure that all observations from a given branch-day cluster are allocated to the same set.
This avoids inferential problems that could arise from correlated unobservables within clusters.
In the first step, we apply the generalized random forest approach of \cite{atheygrf} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
\[
\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
\]
The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step. In particular, we estimate 
\begin{equation}
Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
\label{eq:chernreg}
\end{equation}
where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights. Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
\[
\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
\]
If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. 
Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
Our estimate for $\beta_2$ is 2.5 with a one-sided heteroskedasticity-robust (HC3) of 0.43.
Thus we easily reject the null hypothesis of homogeneous treatment effects.

@@

The \cite{huber_mellace} bounds for the TOT \& TUT APR are respectively:  $[-119, 122]$, and $[-4.2, 24.6]$.
Since both TUT (24) and ToT (122) estimates from the LATE approach lies inside these bounds, we cannot falsify the exclusion restriction. Moreover, the p-values associated with testing violation of inequalities \ref{eq:testable0}, and \ref{eq:testable1} is equal to one in both cases\footnote{We include the implementation of the validity test for the exclusion restriction for choosers and non-choosers in our STATA package.}.

@@

\begin{figure}[H]
        \caption{Example Causal Tree}
    \label{causal_tree1}
    \begin{center}
        \centering
        \includegraphics[width=\textwidth]{Figuras/crf_apr.pdf}
    \end{center}
    \footnotesize 
    This figure shows an example of one of the regression trees used to compute the causal forest estimates described in Section \ref{sec:RF}. Each tree is constructed from a sequence of recursive binary partitions of the covariate space, with a splitting rule that is targeted to the causal quantity of interest, following the methodology of \cite{atheygrf}.
    %This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the fee-forcing contract. It is meant only as an example of how these trees look like. The forest was such that there are as many estimated treatment effects as there are clients.
     %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
\end{figure}

### 2023-10-15 Tables/Attrition.tex
introduce NA in causal RF
tot_tut_validity & edits to the main paper
revision after jpe submission

% Table generated by Excel2LaTeX from sheet 'Attrition'
\begin{tabular}{lcccc}
\toprule
      &       & \multicolumn{3}{c}{Commitment arms} \\
\cmidrule{3-5}      & Control & Forced & Choice & p-value \\
\midrule
\midrule
Number of branch-day pawns & 34    & 34    & 36    & 0.52 \\
      & (3)   & (2.9) & (1.8) &  \\
\multicolumn{1}{p{12.82em}}{Ended up pawning} & 0.98  & 0.97  & 0.97  & 0.62 \\
      & (0.01) & (0.01) & (0.01) &  \\
Survey response rate & 0.79  & 0.76  & 0.77  & 0.62 \\
      & (0.02) & (0.02) & (0.01) &  \\
\midrule
Obs   & 1770  & 1954  & 2580  &  \\
\bottomrule
\bottomrule
\end{tabular}%

>>>>

% Table generated by Excel2LaTeX from sheet 'Attrition'
\begin{tabular}{lcccc}
\toprule
      &       & \multicolumn{3}{c}{Commitment arms} \\
\cmidrule{3-5}      & Control & Forced & Choice & p-value \\
\midrule
\midrule
Number of branch-day pawns & 32    & 34    & 37    & 0.57 \\
      & (3.3) & (2.9) & (3.2) &  \\
\multicolumn{1}{p{12.82em}}{Ended up pawning} & 0.98  & 0.97  & 0.97  & 0.62 \\
      & (0.01) & (0.01) & (0.01) &  \\
Survey response rate & 0.79  & 0.76  & 0.77  & 0.62 \\
      & (0.02) & (0.02) & (0.02) &  \\
\midrule
Obs   & 1770  & 1954  & 2580  &  \\
\bottomrule
\bottomrule
\end{tabular}%
